---
title: "DATA melanoma PROJETM1"
author: "Burgat"
date: "04/03/2021"
output: pdf_document
---
## Analyse des données Melanoma

```{r setup, include=FALSE}
library(readr)
Melanoma <- read_csv("Melanoma.csv")
View(Melanoma)
```


```{r}
library(survival)
library(survminer)
library(ggplot2)
library(ggpubr)
```
#The Melanoma data frame has data on 205 patients in Denmark with malignant melanoma.
#This data frame contains the following columns:
#time
#survival time in days, possibly censored.
#status
#1 died from melanoma, 2 alive, 3 dead from other causes.
#sex
#1 = male, 0 = female.
#age
#age in years.
#year
#of operation.
#thickness
#tumour thickness in mm.
#ulcer
#1 = presence, 0 = absence.

```{r pressure, echo=FALSE}
strata.thickness <- cut(Melanoma$thickness,breaks=c(0,5,20))
z<- survfit(Surv(time, status) ~ strata.thickness, type = "kaplan-meier", conf.type = "plain", Melanoma)
ggsurvplot(z, data = Melanoma)
ggsurvplot(z, fun = "cloglog", data = Melanoma, xlim=c(50,5000))
```


```{r}
fitall<- coxph(Surv(time, status) ~ age + year + ulcer + sex + thickness, data = Melanoma)
ftestall<- cox.zph(fitall)
fitall
ftestall
```


```{r}
fit<- coxph(Surv(time, status) ~ strata.thickness, data = Melanoma)
ftest<- cox.zph(fit, transform = "identity")
plot(ftest, ylim = c(-0.1,0.2), var="strata.thickness", resid=TRUE)
abline(h=0,lty=3)
abline(h=fit$coefficients["sex"], lty=2, lw=2, col="blue")
```


